Does at-issueness predict projection? Further investigations of the Gradient Projection Principle

### 2022-03-14 writing/investigating-GPP.tex
small change

The consequents for the conditional target stimuli in Exps.~1c, 2c, and 3c were created with the following considerations in mind. Each complement clause was paired with a unique consequent clause, as shown in the list below for the 20 complement clauses. Each consequent clause consisted of a uniquely named subject and an adjectival predication in the future tense ({\em will be}); the adjectives all denoted an emotion. We selected the 20 emotion-denoting adjectives based on the following criteria: 10 of the adjectives had a positive valence, and 10 had a negative valence; all 20 adjective had an arousal value between 4.7 and 6.5 (based on the valence and arousal values reported in \citealt{warriner-etal2013}).

@@

The control stimuli in the projection blocks of Exps.~1-3 were formed from the sentences in (1). In Exps.~1, we used the polar question variants of the sentences in (1) in Exp.~1q, and the (positive declarative) sentences in (1) in Exps.~1n, 1m, and 1c; in Exp.~1c, we added the non-restrictive relative clauses (NRRCs) provided in (1) to the respective subjects, so that the control stimuli have two clauses, like the target stimuli.

@@

\begin{table}[h!]
\centering
\begin{tabular}{r l}
Experiment & mean rating \\ 
\hline
1q & .05 \\
2q & .07 \\
3q & .28 \\
\hline
1n & .04 \\
1m & .03 \\
1c & .08 \\
\hline
2n & .22 (16 participants excluded by specified exclusion criterion) \\
2m & .25 \\
2c & .22 \\
\hline
3n & .44  (nobody excluded by specified exclusion criterion) \\
3m & .5 \\
3c & .53 \\
\hline
\end{tabular}
\caption{Mean ratings on at-issueness diagnostics for main clause contents in Exps.~1-3, for self-declared American English participants}\label{t-ai-controls}
\end{table}

>>>>

The consequents for the conditional target stimuli in Exps.~1c, 2c, and 3c were created with the following considerations in mind. Each complement clause was paired with a unique consequent clause, as shown in the list below for the 20 complement clauses. Each consequent clause consisted of a uniquely named subject and an adjectival predication in the future tense ({\em will be}); the adjectives all denoted an emotion. We selected the 20 emotion-denoting adjectives based on the valence and arousal values reported in \citealt{warriner-etal2013}: 10 of the adjectives had a positive valence, and 10 had a negative valence; all 20 adjective had an arousal value between 4.7 and 6.5.

@@

The control stimuli in Exps.~1-3 were main clauses. In Exps.~1n and 1m, we used the sentences in

%in the projection blocks of were formed from the sentences in (1). In Exps.~1, we used the polar question variants of the sentences in (1) in Exp.~1q, and the (positive declarative) sentences in (1) in Exps.~1n, 1m, and 1c; in Exp.~1c, we added the non-restrictive relative clauses (NRRCs) provided in (1) to the respective subjects, so that the control stimuli have two clauses, like the target stimuli.

@@

\begin{table}[h!]
\centering
\begin{tabular}{r l}
Experiment & mean rating \\ 
\hline
1q & .05 \\
2q & .07 \\
3q & .28 \\
\hline
1n & .04 \\
1m & .03 \\
1c & .08 \\
\hline
2n & .22 (16 participants excluded by specified exclusion criterion) \\
2m & .25 \\
2c & .22 \\
\hline
3n & .44  (nobody excluded by specified exclusion criterion) \\
3m & .50 \\
3c & .53 \\
\hline
\end{tabular}
\caption{Mean ratings on at-issueness diagnostics for main clause contents in Exps.~1-3, for self-declared American English participants}\label{t-ai-controls}
\end{table}
